|

### 2021-06-15 01-Chp-Background.Rmd
End of day: -2772

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

@@

### Statins

<!-- TODO Need more on this: maybe a diagram of the pathway -->

<!-- REVIEW [JH] This section seems very short for such a key entity in your thesis. I don’t know exactly what else there is to say about statins, but I recommend expanding it a bit, The second sentence is gobbledygook to me. -->

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA reductase (HMG-CoA-R). This conversion limits the rate at which cholesterol can be produced, enabling statins to reduce effectively the production of LDL cholesterol.

@@

(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the

@@

```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/background/statinPath.png"))
```

@@

&nbsp;
&nbsp;

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

@@

### Statins {#intro-statins}

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R). This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.

@@

(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.

@@

```{r statin-mechanisam, echo = FALSE, results="asis",fig.pos = "H", fig.align = 'center', fig.cap='(ref:statin-mechanisam-cap)', out.width='50%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/background/statinPath.png"))
```

Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)). Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g. ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g. rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]

<!----------------------------------------------------------------------------->
<!-- TODO Review the look and feel of this table -->

(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.

(ref:statinOverview-scaption) Overview of common statins

```{r statinOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

@@

### 2021-06-15 02-Chp-Systematic-Review-Tools.Rmd
End of day: -2772

```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
```

>>>>

```{r medrxivr-sr, echo = FALSE, fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
```

### 2021-06-15 03-Chp-Systematic-Review.Rmd
End of day: -2772

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

As introduced in previous chapters,

<!-- IDEA Evidence map - show the distribution of the different studies population across the world. Distribution will have to be of participants, not primary authors. Though could use to show how data is being used globally -->

## Introduction {#sys-rev-intro}

@@

I systematically search electronic bibliographic databases to identify potentially relevant records. The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy, and detail the specific databases used. See search strategy results. -->

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) Summary of systematic search by topic. For a full list of search terms, see Appendix \@ref()

@@

The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched. <!-- TODO how were these searched? -->

 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

<!-- TODO Look at citationchaser for this, but have a cut-off publication date of  -->

@@

Records weree imported into Endnote and deduplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g. those matched based on the "Title" field alone).

@@

Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]

@@

Participants will be free (or assumed to be free) of dementia/MCI at baseline. Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits will be placed on the sample size of included studies.

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods. Preprints and unpublished reports will be eligible for inclusion if relevant. Multiple publications resulting from the analysis of the same data will be included and grouped.

@@

Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)

@@

@@

we assumed the width of the category to be the same as the adjacent category.
When the lowest category was open ended, we set the lower boundary to zero.

@@

### Search results

Detail

As part of this analysis, we examined the overlap between different published reviews on this topic.

Put upSet plot here.

@@

### Screening results

@@

As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.

@@

For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)). Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeIntra-table)). The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]

@@

```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

Following de-duplication, the titles and abstracts of `r hold()` records were assessed for eligibility. `r hold()` were deemed potentially eligible and the full text records for these were requested and screened. \@ref(fig:prisma-flow-fig)

@@

Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test

@@

###

@@

### Inclusion of preprints

@@

### Open data sharing {#sys-rev-open-data}

@@

### Original contribution to research

@@

### Comparison with other reviews

@@

Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.

@@

<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->

### Reviewing Mendelian randomisations studies

@@

Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for

@@

### Strenghts and limitations

@@

@@

Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]

Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->

Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy. An example is Larsson et al. 2017[@larsson2017a], where the study examined the association between lipid fractions with Azlheimer's disease.

Potentially the use of methods such as snowballing (forwards and backwards citation chasing) should attenuate the bias introduced by this method.

However, in future reviews, a dedicated search for "risk factors" and "dementia" and "

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

The importance of

I found that

The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).

<!----------------------------------------------------------------------------->
## Introduction {#sys-rev-intro}

@@

I systematically search electronic bibliographic databases to identify potentially relevant records. The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. See search strategy results. -->

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) Summary of systematic search by topic. The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range -->

 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->

@@

Records were imported into Endnote and deduplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g. those matched based on the "Title" field alone).

@@

Full-text screening will also be completed in full by the primary author. A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]

@@

Participants were free (or assumed to be free) of dementia/MCI at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits will be placed on the sample size of included studies.

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO do i actually want to include MCI? -->
 For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.

@@

Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)

@@

Multiple publications resulting from the analysis of the same data will be included and grouped ().

@@

I assumed the width of the category to be the same as the adjacent category.
When the lowest category was open ended, I set the lower boundary to zero.

@@

### Search and screening results

`r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.

@@

```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility. `r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened. \@ref(fig:prisma-flow-fig)

@@

As part of our our forward snowballing exercise (where articles citing an included study are cited), Irecorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

<!-- TODO Actually do this! -->

@@

As a summary of the duplication of work in this area, Ilooked at how many reviews a single included study had previously been included in.

@@

For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)). Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)). The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]

@@

@@

Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test

@@

As part of this analysis, Iexamined the overlap between different published reviews on this topic.

<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->

@@

<!----------------------------------------------------------------------------->
### Inclusion of preprints

@@

<!----------------------------------------------------------------------------->
### Open data sharing {#sys-rev-open-data}

@@

<!----------------------------------------------------------------------------->
### Original contribution to research

@@

<!----------------------------------------------------------------------------->
### Comparison with other reviews

@@

Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.

@@

<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->

<!----------------------------------------------------------------------------->
### Reviewing Mendelian randomisations studies

@@

Problems with overlapping samples in reviews of Mendelian randomisation studies in that Imay be double counting participants - for

@@

<!----------------------------------------------------------------------------->
### Strenghts and limitations

@@

<!-- TODO Maybe need to integrate with the section immediately above. Best option probably to move the section above to the end of this section, highlighting that while these studies were included, it was not easy given a lack of resources for MR studies -->

@@

Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy. [@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD. Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic. This may bias reviews as the analysising multiple risk factors at a time becomes more common.

<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->

Is it a big issue that the studies have the same underlying datasets? <!--- TODO check discussion from Matt Lee thesis, in email --->

Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.

### 2021-06-15 04-Chp-CPRD-Analysis.Rmd
End of day: -2772

As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).

@@

>>>>

As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).

@@

<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
